Wikipedia Text Mining and Entropy Analysis

### 2018-12-22 wiki_entropy/wiki_clustering.Rmd
MCA_imputation section added

@@

>>>>

library(missMDA)

@@

```{r MCA_imputation}
wiki_gs <- gs_title("Wikipedia_absolute")
wkpd <- gs_read(wiki_gs) 
LANGUAGES <- wkpd$Language

FEATURES <- c(1:144)
for (i in c(1:144)) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all WALS features in correct syntax

wf.sub <- wf.sub[rowSums(is.na(wf.sub)) != 4, ]
rownames(wf.sub) <- wf.sub$language
wf.sub$language <- NULL
rv <- MIMCA(wf.sub, ncp = 4)

imputed_wf <- as.data.frame(rv[[1]][[99]])
```
